### 2015-01-20 etc/abstract.tex
update

% 1.Statetheproblem
Mutation analysis is a well-known method for measuring the quality of
test suites. However, it is computationally intensive compared to
other measures, which makes it hard to use in practice. Multiple
strategies has been proposed to reduce the number of mutants produced,
and hence reduce the computational requirements.

%
%2.Saywhyit’saninterestingproblem
However, current research on mutation reduction is beset with several
problems. There is inconclusive evidence supporting many of the suggested
reduction strategies due to the limited number and size of of subject
programs investigated. The lack of a comprehensive study comparing
at-least the major approaches is another problem. Finally the traditional
evaluation criteria for mutation reduction approaches relies on
mutation-adequate test suites which rarely occur in real world. There is
little evidence that the strategies that perform well using the traditional
evaluation crtiera leads to better mutation selection for non-adequate
tests in the real world.

@@

We extend the traditional reduction crtieria so that it is usable with
non-mutation adequate test suites, and link it to the actual use of
mutation analysis during development -- to produce tests that check for
as many different bugs as possible.

We evaluate the performance of various selection criteria on 312 opensource
projects from github, which shows that the popular reduction strategies:
operator selection, operator based sampling, and element based sampling
are hardly better than random selection, and often performs worse.
This suggests a need for further research on better methods of mutation
reduction strategies.

% Our results can be used to choose an appropriate mutation
% reduction technique by the reduction and level of fidelity to full
% mutation results required.

%according to the mutation reduction ratio desired, and
%how much reduction in accuracy is acceptable.

@@

% We find that all sampling approaches perform better than operator
% selection methods, when considering ability to predict the full
% mutation score as well as the consistency of mutation reduction ratios
% achieved.

%and also the consistency of mutation reduction ratios achieved.  Specifically,
%we find that random selection of a mutant performs better than statement
%deletion operator selection criteria.

>>>>

% 1.Statetheproblem
Mutation analysis is a well-known method for measuring the quality of
test suites. However, it is computationally intensive compared to other
measures, which makes it hard to use in practice. Multiple strategies have
been proposed to reduce the number of mutants produced, and hence reduce
the computational requirements.

%
%2.Saywhyit’saninterestingproblem
However, current research on mutation reduction is beset with several
problems. There is inconclusive evidence supporting many of the suggested
reduction strategies due to the limited number and size of subject programs
investigated. The lack of a comprehensive study comparing even major approaches
is another problem. Finally the traditional evaluation criteria for mutation
reduction approaches relies on mutation-adequate test suites which rarely occur
in real world. There is little evidence that the strategies that perform well
using the traditional evaluation crtiera leads to better mutation selection
for non-adequate tests in the real world.

@@

We propose a noval evaluation criteria of reduction strategies that is
usable with non-mutation adequate test suites, and link it to the actual
use of mutation analysis during development -- to produce tests that check
for as many different bugs as possible.

We evaluate the performance of various selection strategies on 312 opensource
projects from github, which shows that the popular reduction strategies:
operator selection, stratified sampling of mutations based on operators,
and stratified sampling of mutations based on program elements are hardly
better than random sampling, and often performs worse.  This suggests a need
for further research on better methods of mutation reduction strategies.

@@
